Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-12 apples_and_oranges.qmd
Fixed error resulting in smaller number of med controls than expected

df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))

@@

@@

# count studies
# count the number of studies
n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
# CB checked both, both correct.

>>>>

# We are going to use the descr_active and descr_control columns rather than active_type and control_type columns, as these have unique values for each study. However the descr columns are empty for med studies, so I'm going to paste values across to fix this error.
df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))

df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(descr_control = if_else(is.na(descr_control), control_type, descr_control ))

@@

# I'm going to remove the March / TADS psy control row. It is currently filled with NAs which implies missing data, however it is actually the case that this condition doesn't exist.

df_long_for_metan <- df_long_for_metan %>%
  filter(!(new_study_id == "March, 2004" & is.na(treatment)))

@@

# count studies
# count the number of studies
n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
df_count_studies <- count_studies(df_long_for_metan ) # CHARLOTTE please check
# CB checked both, both correct.
